---
title: "VCS MEMORY"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(cowplot)
theme_set(theme_cowplot())

resp_data <- read.csv(here("..","processed_data","vcs_memory_resp_data_anon_v1.csv"))

```

## SUMMARIZE SUBJECT LEVEL DATA

```{r, warning=F, message=F}
#### summarize subject-level data
subj_response <- resp_data%>%
  group_by(subject,trial_kind,list_id,rotation_start) %>%
  summarize(n=n(),
            outlier_resp=sum(diff_response>60),
            mean_diff=mean(diff_response), 
            mean_abs_diff=mean(abs(diff_response)),
            median_diff=median(diff_response),
            median_abs_diff=median(abs(diff_response)),
            mean_rt=mean(rt),
            median_rt=median(rt),
            exclude=exclude[1])

subj_response  %>%
  arrange(subject,trial_kind) %>%
  DT::datatable()
```

###  Handle participant-level and trial-level exclusions

Excluding 9 participants who havea disproportionate number of apparently random responses.

```{r, warning=F, message=F}
#exclude participants
resp_data_exclusions <- resp_data %>%
  filter(exclude=="n")
subj_response_clean <- subj_response %>%
  filter(exclude=="n")
```

Excluding outlier trials (>60 degree difference). About `r round(mean(abs(resp_data_exclusions$diff_response)>60),4)*100`% of remaining trials.

``` {r}
#exclude responses over 60 (~3%)
resp_data_clean <- resp_data_exclusions %>%
  filter(abs(diff_response)<=60)
```


## DESCRIPTIVE PLOTS  {.tabset}

### Difference in Response (All Trials)

Difference in response from target shape for all trials, with smoothed fit across all data.

```{r, warning=F, message=F}
ggplot(resp_data_clean,aes(x=correct_response,y=diff_response))+
  geom_jitter(alpha=0.15)+
  geom_hline(yintercept=0,size=1.2,color="firebrick")+
  geom_smooth()+
  facet_wrap(~trial_kind)
ggsave(here("figures","vcs_memory_difference_response.pdf"), width=9,  height=6)
```

### Histogram in response frequency by item/ shape

``` {r, warning=F, message=F}
summarize_response_location <- resp_data %>%
  count(trial_kind,response)

ggplot(summarize_response_location,aes(response,n))+
  geom_histogram(stat="identity")+
  #geom_vline(xintercept=seq(0,360,10),color="red")+
  facet_wrap(~trial_kind)
```

## Item-Wise Analysis

Average response bias by item/ shape

```{r, warning=F, message=F}
#### item-wise analysis ####
item_response <- resp_data_clean %>%
  group_by(correct_response,trial_kind) %>%
  summarize(
    N=n(),
    mean_diff=mean(diff_response),
    sd_diff=sd(diff_response),
    mean_abs_diff=mean(abs(diff_response)),
    sd_abs_diff=sd(abs(diff_response)),
    simpson_diversity=simpson_diversity[1],
    modal_agreement=modal_agreement[1],
    modal_response_agreement=modal_response_agreement[1],
  )

ggplot(item_response,aes(correct_response,mean_diff))+
  geom_point()+
  geom_smooth(method="gam")+
  #geom_smooth(aes(y=sd_diff),color="red")+
  geom_line(aes(y=modal_agreement*10),col="red")+
  #geom_line(aes(y=modal_response_agreement*10),col="purple")+
  geom_line(aes(y=simpson_diversity*10),col="green")+
  facet_wrap(~trial_kind)
```

Smoothing in the plot uses GAMS. 
The colored lines indicate various measures of nameability (scaled up for visibility on the y-axis). 

Red = Modal Agreement.

Green = Simpson Diversity.

### Response Difference By Start Value

```{r, warning=F, message=F}
ggplot(filter(resp_data_clean,trial_kind=="delayed"&abs(diff_response)<30),aes(x=start_value,y=diff_response))+
  geom_jitter(alpha=0.15)+
  geom_hline(yintercept=0,size=1.2,color="firebrick")+
  geom_smooth(method="loess")+
  geom_vline(aes(xintercept=correct_response))+
  facet_wrap(~correct_response)
```

